SSA based global code motion of identical computations

### 2017-04-16 acmart-pacmpl-template.tex
remove separate profitability args

\subsubsection{Profitability of hoisting scalars}
Since scalars are the majority of instructions which are hoisted, we pay special
attention in case of hoisting scalars too far, as that may increase register
pressure and result in spills. For example hoisting a scalar past a call, as
described in Section~\ref{cost:across-calls}.  In our current implementation we
hoist scalars past a call only when optimizing for code-side (-Os). Ideally, a
later stage of live-range splitting pass should split the live-ranges for
optimal performance, however, that is not the case with \LLVM{} as we have found
regressions when scalars are hoisted too far, as in
Section~\ref{sec:cost-models}. Another way to mitigate this problem is be to
reinstantiate (rematerialize) the computation after a call (may be as a
different optimization pass).

\subsubsection{Profitability of hoisting loads}
A load instruction introduces a register where the value loaded will be kept,
the register pressure increases by one (unless the operand to load becomes dead
at the load). On the other hand, loading a value early will reduce the stall
during execution should the value is not in the cache. We generally prefer to
hoist load except when the hoisting point is too far (this distance is computed by
looking at the experimental results of representative benchmarks, see
Section~\ref{sec:experimental-results}).

\subsubsection{Profitability of hoisting stores}
Since stores do not increase the live-range of any registers, and in some cases
it ends the liveness of registers, we hoist all the stores.

\subsubsection{Profitability of hoisting calls}
Currently we hoist all the calls that are suitable candidates for hoisting.

Since stores and calls are hoisted the least \ref{table:experimental-results}
the performance does not change much whether they are hoisted or not.

>>>>

There is a special case for hoisting load instructions when the hoist-point is
the predecessor basic block for all the loads. Even if the register pressure
would increase, we prefer to hoist loads in this case. The reason being, that
would make the loaded value available by the time it is used. Also, because
stores and calls are hoisted the least \ref{table:experimental-results}, the
performance does not change much whether they are hoisted or not.
